Programmable, Efficient and Scalable Secure Two-Party Computation for Machine Learning

### 2018-08-06 ndss/eval.tex
minor

We present the numbers for two network settings, a LAN setting and
a cross-continent WAN setting. The round trip time between the server
and the client machines in the two settings is 1ms and 40ms respectively. Each
machine has an Intel(R) Xeon(R) CPU E5-2673 v3 processor running at
2.40GHz with 28 GBs of RAM. When we compare our execution times with prior protocols, we match our system and network parameters with those of the prior work (as the code for works such as Bost et al. \cite{shafindss} and \minion~\cite{minionn} are not publicly available).
%
%% The  \tool compiler is written in Python and
%% compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
%% library~\cite{aby}. We use an off-the-shelf solver
%% (SeaHorn~\cite{seahorn}) to check the verification conditions required
%% to prove that the array indices remain in bound. The solver takes less
%% than a minute on our largest benchmark.
Most of our benchmarks
are related to machine learning. We set up (largely standard) notation and describe our benchmarks in \appendixref{benchmarks}.

>>>>

We present the numbers for two network settings, a LAN setting and
a cross-continent WAN setting. The round trip time between the server
and the client machines in the two settings is 1ms and 40ms respectively. Each
machine has an Intel(R) Xeon(R) CPU E5-2673 v3 processor running at
2.40GHz with 28 GBs of RAM. When we compare our execution times with prior protocols, we match our system and network parameters with those of the prior work (these implementations are not publicly available).
%
%% The  \tool compiler is written in Python and
%% compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
%% library~\cite{aby}. We use an off-the-shelf solver
%% (SeaHorn~\cite{seahorn}) to check the verification conditions required
%% to prove that the array indices remain in bound. The solver takes less
%% than a minute on our largest benchmark.
Most of our benchmarks
are related to machine learning. We set up (largely standard) notation and describe our benchmarks in \appendixref{benchmarks}.

### 2018-08-06 ndss/intro.tex
minor

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed either as a boolean
circuit~(\cite{yao,gmw}) or as an arithmetic circuit~(\cite{sss,viff,gentry}). 
%
\dg{Do we want to say sharemind? It is only 3PC.}
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can either be expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
It is well-known that boolean circuits are not suitable for doing arithmetic operations such as integer multiplications but are unavoidable for boolean operations such as comparison \cite{aby,tasty,autoS,secureml,minionn,chameleon}.
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%

@@

\subsection{Related Work}
Before ABY~\cite{aby}, several works have proposed
combining secure computation protocols based on homomorphic
encryption and Yao's garbled circuits
(e.g. \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}),
and some have also developed tools that allow writing such
combinations (e.g. \cite{bogdanov,lone,tasty,autoS}). However, as Demmler et
al.~\cite{aby} observe, due
 to the high conversion cost between
homomorphic encryption and Yao's garbled circuits, these combined
protocols do not gain much performance over a single
protocol. 
Additionally, these prior works provide informal languages
or libraries that lack formal semantics and static guarantees.
Finally, we focus on the language
features necessary to implement machine learning applications.
In particular, we do not discuss declassification of
intermediate values or indexing into arrays at secret indices.
 Handling them requires additional complexity. For example,
Wysteria~\cite{wysteria} handles the former using dependent types
and ObliVM~\cite{oblivm} uses Oblivious RAM for the latter.
These situations seldomly arise in the machine learning applications that we consider:
intermediate values don't need to be declassified and arrays are traversed in an oblivious manner. We provide a detailed survey of related
work in \sectionref{related}.

>>>>

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed either as a boolean
circuit~(\cite{yao,gmw}) or as an arithmetic circuit~(\cite{sss,viff,gentry}). 
%
%\dg{Do we want to say sharemind? It is only 3PC.}
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can either be expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
It is well-known that boolean circuits are not suitable for doing arithmetic operations such as integer multiplications but are unavoidable for boolean operations such as comparison \cite{aby,tasty,autoS,secureml,minionn,chameleon}.
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%

@@

\subsection{Related Work}
Before ABY~\cite{aby}, several works have proposed
combining secure computation protocols based on homomorphic
encryption and Yao's garbled circuits
(e.g. \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}),
and some have also developed tools that allow writing such
combinations (e.g. \cite{bogdanov,lone,tasty,autoS}). However, as Demmler et
al.~\cite{aby} observe, due
 to the high conversion cost between
homomorphic encryption and Yao's garbled circuits, these combined
protocols do not gain much performance over a single
protocol. 
Additionally, these prior works provide informal languages
or libraries that lack formal semantics and static guarantees.
Finally, we focus on the language
features necessary to implement machine learning applications.
In particular, we do not discuss declassification of
intermediate values or indexing into arrays at secret indices.
 Handling them requires additional complexity. For example,
Wysteria~\cite{wysteria} handles the former using dependent types
and ObliVM~\cite{oblivm} uses Oblivious RAM for the latter.
These situations seldomly arise in the machine learning applications that we consider:
intermediate values don't need to be declassified and arrays are mostly traversed in an oblivious manner. We provide a detailed survey of related
work in \sectionref{related}.

### 2018-08-06 ndss/ld.tex
ccs comments.
minor

To prove the correctness of \tool, we prove that  the observations in
source semantics and the distributed circuit semantics are identical
(\theoremref{correctness}).
We combine this correctness theorem and the security of the \mpc
back-end to prove security of the protocols generated by \tool
(\theoremref{security}).
%For the security of our compiler, we rely on the correctness guarantee and  reduce the security to the security of the underlying cryptographic protocol used to compute the generated circuit (see \theoremref{security}).
We present only selected parts of our formalization. Full definitions, auxiliary lemmas and complete proofs can be found in the full version of this paper. %We will also
%release complete typeset proofs in a tech report.

@@

We prove the theorem in the full version. %Appendix~\ref{app:formal}.
% We first define a judgment for
%translation of environments, $\Gamma \vdash \rho \leadsto
%\widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$. The
%judgment is defined inductively on $\Gamma$, and establishes that
%the static environment $\Gamma$ is consistent with the runtime
%environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho}_{1}$ and
%$\widehat{\rho}_{2}$. 
%As an example, if $x:\kw{uint}^{\mathcal{P}} \in
%\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
%n$, for some $n$. On the other hand, if $x:\kw{uint}^{m} \in
%\Gamma$ then the judgment checks that $\mathcal{D}_m( \widehat{\rho}_{1}(\widetilde{\rho}(x)),\widehat{\rho}_{2}(\widetilde{\rho}(x)))=\rho(x)$.
%%We elide the judgment, providing the full definition
%%in the supplementary material.
%With this judgment,
%the correctness theorem is as follows:
%
%\begin{theorem}[Correctness]\label{theorem:correctness}
%  $\forall\:\Gamma, s, \widetilde{s}, \Gamma_{1}, \rho, \widetilde{\rho}, \widehat{\rho}_{1}, \widehat{\rho}_{2}$, if:
%
%  \begin{enumerate}
%  \item $\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$
%  \item $\Gamma \vdash \rho \leadsto \widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$
%  \end{enumerate}
%
%  then $\exists \rho_{1}, O_{1}, \widetilde{\rho}_{1}, \chi, \widehat{\rho}'_{1}, \widehat{\rho}'_{2}, O_{2}$, s.t.
%
%  \begin{enumerate}[label=(\alph*)]
%  \item $\rho \vdash s \Downarrow \rho_{1}; O_{1}$
%  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}_{1}; \chi$
%  \item $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O_{2}$
%  \item $\Gamma_{1} \vdash \rho_{1} \leadsto \widetilde{\rho}_{1}; \widehat{\rho}'_{1}, \widehat{\rho}'_{2}$
%  \item $O_{1} = O_{2}$
%  \end{enumerate}
%  
%\end{theorem}
%
%The theorem states that if a source statement $s$ is well-typed, and
%compiles to $\widetilde{s}$ in intermediate language, then $s$ terminates in the source
%semantics with observations $O_{1}$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the
%circuit semantics with observations $O_{2}$, where $O_{1} = O_{2}$
%%Furthermore, the final environments are also in the compilation
%%relation. \divya{Should we call the judgment between environs as compilation relation?}
%Due to space reasons, we provide the proof in \cite{anonymized}.

>>>>

To prove the correctness of \tool, we prove that  the observations in
source semantics and the distributed circuit semantics are identical
(\theoremref{correctness}).
We combine this correctness theorem and the security of the \mpc
back-end to prove security of the protocols generated by \tool
(\theoremref{security}).
%For the security of our compiler, we rely on the correctness guarantee and  reduce the security to the security of the underlying cryptographic protocol used to compute the generated circuit (see \theoremref{security}).
We present only selected parts of our formalization. Full definitions, auxiliary lemmas and complete proofs (that follow from a straight-forward induction argument once the key lemmas are identified) can be found in the full version of this paper. %We will also
%release complete typeset proofs in a tech report.

@@

We prove the theorem in the full version by induction on the compilation derivation. %Appendix~\ref{app:formal}.
% We first define a judgment for
%translation of environments, $\Gamma \vdash \rho \leadsto
%\widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$. The
%judgment is defined inductively on $\Gamma$, and establishes that
%the static environment $\Gamma$ is consistent with the runtime
%environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho}_{1}$ and
%$\widehat{\rho}_{2}$. 
%As an example, if $x:\kw{uint}^{\mathcal{P}} \in
%\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
%n$, for some $n$. On the other hand, if $x:\kw{uint}^{m} \in
%\Gamma$ then the judgment checks that $\mathcal{D}_m( \widehat{\rho}_{1}(\widetilde{\rho}(x)),\widehat{\rho}_{2}(\widetilde{\rho}(x)))=\rho(x)$.
%%We elide the judgment, providing the full definition
%%in the supplementary material.
%With this judgment,
%the correctness theorem is as follows:
%
%\begin{theorem}[Correctness]\label{theorem:correctness}
%  $\forall\:\Gamma, s, \widetilde{s}, \Gamma_{1}, \rho, \widetilde{\rho}, \widehat{\rho}_{1}, \widehat{\rho}_{2}$, if:
%
%  \begin{enumerate}
%  \item $\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$
%  \item $\Gamma \vdash \rho \leadsto \widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$
%  \end{enumerate}
%
%  then $\exists \rho_{1}, O_{1}, \widetilde{\rho}_{1}, \chi, \widehat{\rho}'_{1}, \widehat{\rho}'_{2}, O_{2}$, s.t.
%
%  \begin{enumerate}[label=(\alph*)]
%  \item $\rho \vdash s \Downarrow \rho_{1}; O_{1}$
%  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}_{1}; \chi$
%  \item $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O_{2}$
%  \item $\Gamma_{1} \vdash \rho_{1} \leadsto \widetilde{\rho}_{1}; \widehat{\rho}'_{1}, \widehat{\rho}'_{2}$
%  \item $O_{1} = O_{2}$
%  \end{enumerate}
%  
%\end{theorem}
%
%The theorem states that if a source statement $s$ is well-typed, and
%compiles to $\widetilde{s}$ in intermediate language, then $s$ terminates in the source
%semantics with observations $O_{1}$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the
%circuit semantics with observations $O_{2}$, where $O_{1} = O_{2}$
%%Furthermore, the final environments are also in the compilation
%%relation. \divya{Should we call the judgment between environs as compilation relation?}
%Due to space reasons, we provide the proof in \cite{anonymized}.
